>

### 2020-09-22 manuscript/manuscript.Rmd
Remove discussion of cemeteries from data assembly

In a destination choice framework, the tracts represent the "origins" and the
"destinations" are parks and green spaces in New York City.
We retrieved a polygons layer of public parks and green spaces within New York City’s
municipal boundaries and checked it for accuracy and relevance [@nycparks].
Upon inspection, we removed several facilities that do not qualify as
publicly accessible green space, such as Yankee Stadium, Citi Field, and their
surrounding parking lots. We also removed parks of less than half an acre in
size, as these appear to be predominantly planted medians rather than legitimate
public green space. We consolidated individual geographic polygons
comprising a single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields included within
larger park facilities. Instead of these distinct sub-facilities, we created 
variables for each containing park indicating the presence of sports courts,
playgrounds, and trails.

To this dataset of parks and regularized green spaces, we add a polygons layer of
cemeteries in New York that are open to the public. Cemeteries are important
green spaces that can be used for many types of physical activity. These
operations leave us with `r nrow(parks)` distinct green spaces; for simplicity 
we will refer to both parks and cemeteries as "parks" going forward. 
For each park, we calculate the size of the park in acres.

>>>>

In a destination choice framework, the tracts represent the "origins" and the
"destinations" are parks and green spaces in New York City.
We retrieved a polygons layer of public parks and green spaces within New York City’s
municipal boundaries and checked it for accuracy and relevance [@nycparks].
Upon inspection, we removed several facilities that do not qualify as
publicly accessible green space, such as Yankee Stadium, Citi Field, and their
surrounding parking lots. We also removed parks of less than half an acre in
size, as these appear to be predominantly planted medians rather than legitimate
public green space. We consolidated individual geographic polygons
comprising a single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields included within
larger park facilities. Instead of these distinct sub-facilities, we created 
variables for each containing park indicating the presence of sports courts,
playgrounds, and trails. These operations leave us with `r nrow(parks)` distinct
green spaces; For each park, we calculate the size of the park in acres.
